---
title: "mh_exploration"
author: Jeffrey Choi
output: html_document
---

Let's look into clustering the change in centile scores
```{r}
library(dplyr)
library(longCombat)
library(forcats)
library(gamlss)
library(gamlss.data)
library(gamlss.dist)
library(gamlss.foreach)
library(gamlss.ggplots)
```

Data preproccessing
```{r}
#| warning: false

# mental health df from Initial_Data_Cleaning.rmd
mh_data <- read.csv("/Users/jeffee/Library/CloudStorage/Box-Box/ABCD Data/2025-07-01_JC.csv")

# lets work with cortical thickness first
data_dir <- '/Users/jeffee/Library/CloudStorage/Box-Box/ABCD Tabulated Data/5.1/core/'

setwd(data_dir)

# LOAD DATA
# Demographic variables and propensity weights
demog <- read.csv("abcd-general/abcd_p_demo.csv", na.strings = c(999, 777))
# Age in months, Site ID (ABCD Study Design Variables), Family ID
study_covars <- read.csv("abcd-general/abcd_y_lt.csv")
# desikan atlas, cortical thickness
dat.mri.ct = read.csv('imaging/mri_y_smr_thk_dsk.csv')

list_of_ct_regions <- colnames(dat.mri.ct)[3:ncol(dat.mri.ct)] # this is important


# basic cleaning for demographic variables
demog_clean <- demog |>
  # select broad demographics
  select(src_subject_id, eventname, starts_with("demo_brthdat_v2"), demo_sex_v2, race_ethnicity) |>
  # fill in race and sex first (avoid losing demog info due to filtering eventname)
  group_by(src_subject_id) %>%
  mutate(
    race_ethnicity = first(na.omit(race_ethnicity)),
    demo_sex_v2 = first(na.omit(demo_sex_v2)),
    src_subject_id = factor(src_subject_id)
  ) %>%
  ungroup() %>%
  filter(eventname %in% c("baseline_year_1_arm_1", "2_year_follow_up_y_arm_1",
                          "4_year_follow_up_y_arm_1")) |>
  mutate(
    # clean age variable
    age = case_when(
      eventname == "baseline_year_1_arm_1" ~ trunc(demo_brthdat_v2), # remove decimals 
      eventname %in% c("2_year_follow_up_y_arm_1", "4_year_follow_up_y_arm_1") ~
        trunc(demo_brthdat_v2_l)),
    # broad race/ethnicity categories
    race_ethnicity = case_match(
      race_ethnicity,
      1 ~ "White",
      2 ~ "Black",
      3 ~ "Hispanic",
      4 ~ "Asian",
      5 ~ "Other"
    ),
    # recode sex variable
    sex = factor(demo_sex_v2),
    sex = fct_recode(
      sex,
      "Intersex-Male" = "3"
    )) %>%
  filter(eventname %in% c("baseline_year_1_arm_1", "2_year_follow_up_y_arm_1",
                          "4_year_follow_up_y_arm_1"))


thickness <- dat.mri.ct |>
  # join mri data to demographics
  left_join(demog_clean, by = join_by("eventname", "src_subject_id")) |>
  # join to study covariates
  left_join(study_covars, by = join_by("eventname", "src_subject_id")) |>
  select(src_subject_id, eventname, starts_with("smri"), age, sex, race_ethnicity 
         , site_id_l, interview_age) |>
  # remove ages less than 8 and more than 16
  filter(age < 16 & age > 8) |>
  mutate(interview_age = as.numeric(interview_age))

# create baseline age column for longComBat
baseline_ages <- thickness %>%
  mutate(baseline_age = interview_age / 12) %>%
  group_by(src_subject_id) %>%
  mutate(baseline_age = first(baseline_age)) %>%
  pull(baseline_age)

# removed single NA race and intersex individuals (3)
thickness <- thickness %>%
  mutate(baseline_age = baseline_ages) %>%
  filter(sex != "Intersex-Male") %>%
  filter(!is.na(race_ethnicity))
```

```{r}
if("package:tidyverse" %in% search()){
  detach("package:tidyverse", unload = TRUE)
}

library(longCombat)

simdata_combat <- longCombat(idvar='src_subject_id', 
                             timevar='interview_age',
                             batchvar='site_id_l', 
                             features=list_of_ct_regions, 
                             formula='sex + baseline_age',
                             ranef='(1|src_subject_id)', # random individual effect intercept
                             data=thickness)
```
```{r}
library(tidyverse)
```

```{r}
thickness_harmonized <- simdata_combat$data_combat

thickness_plus_harmonized <- merge(thickness, thickness_harmonized, by=c('src_subject_id', "interview_age", "site_id_l"))
thickness_plus_harmonized <- thickness_plus_harmonized %>% mutate(src_subject_id = factor(src_subject_id))

# adds sex and other cols
thickness_harmonized <- thickness_plus_harmonized %>%
  select(-matches("^smri(?!.*\\.combat$)", perl = TRUE)) %>% 
  mutate(src_subject_id = factor(src_subject_id))

# groups by sex
# ONLY USE MEAN COL
thickness_harmonized_male <- thickness_harmonized %>% 
  filter(sex == 2) %>%
  select(src_subject_id, interview_age, race_ethnicity, smri_thick_cdk_mean.combat)

thickness_harmonized_female <- thickness_harmonized %>%
  filter(sex == 1) %>%
  select(src_subject_id, interview_age, race_ethnicity, smri_thick_cdk_mean.combat)

# used to get power for x transformation
lms_model_m <- lms(smri_thick_cdk_mean.combat, 
                 interview_age, 
                 data = thickness_harmonized_male, 
                 trans.x = TRUE, 
                 k = 2)

lms_model_f <- lms(smri_thick_cdk_mean.combat, 
                 interview_age, 
                 data = thickness_harmonized_female, 
                 trans.x = TRUE, 
                 k = 2)
```

## Model 21 - family: Box-Cox t (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model21_male <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model21_female <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age^lms_model_f$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized_female)
```

## Model 21 Male Statistics - family: Box-Cox t (power transformation on predictor)
```{r}
#| warning: false

summary(thickness_model21_male)

fitted_centiles_legend(
  thickness_model21_male,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model21_male,
  xvar = thickness_harmonized_male$interview_age,
  zvals = TRUE), 3)

wp(thickness_model21_male, xvar = thickness_harmonized_male$interview_age)
```

## Model 21 Female Statistics - family: Box-Cox t (power transformation on predictor)
```{r}
#| warning: false

summary(thickness_model21_female)

fitted_centiles_legend(
  thickness_model21_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model21_female,
  xvar = thickness_harmonized_female$interview_age,
  zvals = TRUE), 3)
```

```{r}
# Collecting centile scores for overall mean male
thickness_harmonized_male_newdata <- thickness_harmonized_male

# having newdata gives an assumption warning? idk just commented it out
thickness_harmonized_male$mu <- predict(thickness_model21_male,
                                        what = "mu",
                                        #newdata = thickness_harmonized_male,
                                        type = "response")

thickness_harmonized_male$sigma <- predict(thickness_model21_male,
                                           what = "sigma",
                                           #newdata = thickness_harmonized_male,
                                           type = "response")

thickness_harmonized_male$nu <- predict(thickness_model21_male,
                                        what = "nu",
                                        #newdata = thickness_harmonized_male,
                                        type = "response")

thickness_harmonized_male$tau <- predict(thickness_model21_male,
                                        what = "tau",
                                        #newdata = thickness_harmonized_male,
                                        type = "response")

thickness_harmonized_male$centile <- with(thickness_model21_male,
                                                  pBCT(thickness_harmonized_male$smri_thick_cdk_mean.combat,
    mu = thickness_harmonized_male$mu,
    sigma = thickness_harmonized_male$sigma,
    nu = thickness_harmonized_male$nu,
    tau = thickness_harmonized_male$tau))


thickness_harmonized_male$fitted <- fitted(thickness_model21_male,
                                        what = "mu",
                                        type = "response")
thickness_harmonized_male$residual <- 
  thickness_harmonized_male$smri_thick_cdk_mean.combat - thickness_harmonized_male$fitted
```


```{r}
# Collecting centile scores for overall mean female
thickness_harmonized_female$mu <- predict(thickness_model21_female,
                                        what = "mu",
                                        #newdata = thickness_harmonized_female,
                                        type = "response")

thickness_harmonized_female$sigma <- predict(thickness_model21_female,
                                           what = "sigma",
                                           #newdata = thickness_harmonized_female,
                                           type = "response")

thickness_harmonized_female$nu <- predict(thickness_model21_female,
                                        what = "nu",
                                        #newdata = thickness_harmonized_female,
                                        type = "response")

thickness_harmonized_female$tau <- predict(thickness_model21_female,
                                        what = "tau",
                                        #newdata = thickness_harmonized_female,
                                        type = "response")

thickness_harmonized_female$centile <- with(thickness_model21_female,
                                                    pBCT(thickness_harmonized_female$smri_thick_cdk_mean.combat,
    mu = thickness_harmonized_female$mu,
    sigma = thickness_harmonized_female$sigma,
    nu = thickness_harmonized_female$nu,
    tau = thickness_harmonized_female$tau))

thickness_harmonized_female$fitted <- fitted(thickness_model21_female,
                                        what = "mu",
                                        type = "response")
thickness_harmonized_female$residual <- 
  thickness_harmonized_female$smri_thick_cdk_mean.combat - thickness_harmonized_female$fitted

```

```{r}
# adds eventname into df for pivot widering
thickness_centile_male <- thickness_harmonized_male %>%
  left_join(thickness_harmonized %>%
              filter(sex == 2) %>%
              select(src_subject_id, interview_age, eventname, ),
            by = c("src_subject_id", "interview_age"))

thickness_centile_female <- thickness_harmonized_female%>%
  left_join(thickness_harmonized %>%
              filter(sex == 1) %>%
              select(src_subject_id, interview_age, eventname),
            by = c("src_subject_id", "interview_age"))
```


```{r}
thickness_centile_male_wider <- thickness_centile_male %>%
  select(
    src_subject_id, eventname, interview_age,
    smri_thick_cdk_mean.combat, centile, race_ethnicity
  ) %>%
  pivot_wider(
    names_from = eventname,
    values_from = c(interview_age, smri_thick_cdk_mean.combat, centile)
  ) %>%
  rename(
    interview_age_baseline = interview_age_baseline_year_1_arm_1,
    interview_age_year_2 = interview_age_2_year_follow_up_y_arm_1,
    interview_age_year_4 = interview_age_4_year_follow_up_y_arm_1,
    smri_thick_cdk_mean.combat_baseline = smri_thick_cdk_mean.combat_baseline_year_1_arm_1,
    smri_thick_cdk_mean.combat_year_2 = smri_thick_cdk_mean.combat_2_year_follow_up_y_arm_1,
    smri_thick_cdk_mean.combat_year_4 = smri_thick_cdk_mean.combat_4_year_follow_up_y_arm_1,
    centile_baseline = centile_baseline_year_1_arm_1,
    centile_year_2 = centile_2_year_follow_up_y_arm_1,
    centile_year_4 = centile_4_year_follow_up_y_arm_1,
    )

thickness_centile_female_wider <- thickness_centile_female %>%
  select(
    src_subject_id, eventname, interview_age,
         smri_thick_cdk_mean.combat, centile, race_ethnicity
    ) %>%
  pivot_wider(
    names_from = eventname,
    values_from = c(interview_age, smri_thick_cdk_mean.combat, centile)
    ) %>%
  rename(
    interview_age_baseline = interview_age_baseline_year_1_arm_1,
    interview_age_year_2 = interview_age_2_year_follow_up_y_arm_1,
    interview_age_year_4 = interview_age_4_year_follow_up_y_arm_1,
    smri_thick_cdk_mean.combat_baseline = smri_thick_cdk_mean.combat_baseline_year_1_arm_1,
    smri_thick_cdk_mean.combat_year_2 = smri_thick_cdk_mean.combat_2_year_follow_up_y_arm_1,
    smri_thick_cdk_mean.combat_year_4 = smri_thick_cdk_mean.combat_4_year_follow_up_y_arm_1,
    centile_baseline = centile_baseline_year_1_arm_1,
    centile_year_2 = centile_2_year_follow_up_y_arm_1,
    centile_year_4 = centile_4_year_follow_up_y_arm_1,
    )
```

```{r}
# joining with mental health data
thickness_centile_male_mh <- thickness_centile_male %>%
  select(src_subject_id, eventname, interview_age, smri_thick_cdk_mean.combat, centile) %>% 
  left_join(mh_data, by = join_by("src_subject_id", "eventname", "interview_age"))

thickness_centile_female_mh <- thickness_centile_female %>%
  select(src_subject_id, eventname, interview_age, smri_thick_cdk_mean.combat, centile) %>% 
  left_join(mh_data, by = join_by("src_subject_id", "eventname", "interview_age"))
```

```{r}
thickness_centile_male_wider <- thickness_centile_male %>% 
  group_by(src_subject_id) %>%
  mutate(interview_age_centered = interview_age - 108) %>% 
  nest() %>% 
  mutate(model = map(data, ~ lm(centile ~ interview_age_centered, data = .)),
         result = map(model, function(x) list(intercept= x$coef[1],
                                              slope = x$coef[2],
                                              rsq = summary(x)$r.squared))) %>% 
  unnest_wider(result) %>% 
  select(src_subject_id, model, intercept, slope, rsq) %>% 
  left_join(thickness_centile_male_wider, by = "src_subject_id")

```

```{r}
set.seed(118)  # for reproducibility

thickness_centile_male_wider_na <- thickness_centile_male_wider %>% 
  filter(!is.na(slope))

thickness_centile_male_wider_na$intercept_scaled <-
  as.numeric(scale(thickness_centile_male_wider_na$intercept))
thickness_centile_male_wider_na$slope_scaled     <-
  as.numeric(scale(thickness_centile_male_wider_na$slope))


kmeans <- kmeans(thickness_centile_male_wider_na[, c("slope_scaled", "intercept_scaled")], 4)
thickness_centile_male_wider_na$centile_cluster_km <- kmeans$cluster

thickness_centile_male_wider_na %>%
  ggplot(aes(x = intercept, y = slope, color = factor(centile_cluster_km))) +
  geom_point(size = 2) +
  geom_vline(xintercept = mean(thickness_centile_male_wider_na$intercept),
             linetype = "dashed", color = "black") +
  labs(x = "Intercept at Age 9 (108 Months)",
       y = "Slope",
       color = "Cluster")

```


```{r}
hc_average <- hclust(dist(thickness_centile_male_wider_na[, c("slope_scaled", "intercept_scaled")]),
                     method = "average")

thickness_centile_male_wider_na$centile_cluster_hc <- cutree(hc_average, k = 6)

thickness_centile_male_wider_na %>%
  ggplot(aes(x = intercept, y = slope, color = factor(centile_cluster_hc))) +
  geom_point(size = 2) +
  geom_vline(xintercept = mean(thickness_centile_male_wider_na$intercept),
             linetype = "dashed", color = "black") +
  labs(x = "Intercept at Age 9 (108 Months)",
       y = "Slope",
       color = "Cluster")
```
Plotting some results from the clusters
```{r}
thickness_centile_male_wider_na %>%
  ggplot(aes(x = intercept, y = slope, color = factor(centile_cluster_km))) +
  geom_point(size = 2) +
  geom_vline(xintercept = mean(thickness_centile_male_wider_na$intercept),
             linetype = "dashed", color = "black") +
  labs(x = "Intercept at Age 9 (108 Months)",
       y = "Slope",
       color = "Cluster")

thickness_centile_male_wider_na %>%
  drop_na() %>%
  ggplot(aes(x = centile_cluster_km, fill = race_ethnicity)) +
  geom_bar(position = "stack") +
  labs(title = "Race Count By Centile Clusters",
       x = "Cluster",
       y = "Individual Count")

thickness_centile_male_wider_na %>%
  group_by(centile_cluster_km, race_ethnicity) %>%
  summarize(count = n()) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = factor(centile_cluster_km), y = prop, fill = race_ethnicity)) +
  geom_col(position = "fill") +
  labs(title = "Race Proportions by Cluster",
       x = "Cluster",
       y = "Proportion")
```

```{r}
thickness_centile_male_wider_na %>%
  group_by(centile_cluster_km, demo_comb_income_v2_comb) %>%
  summarize(count = n()) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = factor(centile_cluster_km), y = prop, fill = demo_comb_income_v2_comb)) +
  geom_col(position = "fill") +
  labs(title = "Income Proportions by Cluster",
       x = "Cluster",
       y = "Proportion")

```
```{r}
thickness_centile_male_wider_na %>%
  left_join(thickness_centile_male_mh %>%
              group_by(src_subject_id) %>%
              summarize(demo_comb_income_v2_comb = first(na.omit(demo_comb_income_v2_comb)))
          , by = "src_subject_id") %>% 
  mutate(income_simple = case_when(
    demo_comb_income_v2_comb %in% 1:4   ~ 1,  # < $25k
    demo_comb_income_v2_comb %in% 7:8   ~ 2,  # $50k–$99k
    demo_comb_income_v2_comb == 10      ~ 4,  # > $200k
    demo_comb_income_v2_comb %in% c(5,6,9) ~ 3,  # everyone else
    demo_comb_income_v2_comb %in% c(777, 999) ~ NA  # missing responses
  )) %>% 
  mutate(income_simple = factor(income_simple)) %>% 
  filter(!is.na(income_simple)) %>% 
  ggplot(aes(x = centile_cluster_km, fill = income_simple)) +
  geom_bar(position = "stack") +
  labs(title = "Income Counts by Cluster",
       x = "Cluster",
       y = "Individual Counts")


thickness_centile_male_wider_na %>%
  left_join(thickness_centile_male_mh %>%
              group_by(src_subject_id) %>%
              summarize(demo_comb_income_v2_comb = first(na.omit(demo_comb_income_v2_comb)))
          , by = "src_subject_id") %>% 
  mutate(income_simple = case_when(
    demo_comb_income_v2_comb %in% 1:4   ~ 1,  # < $25k
    demo_comb_income_v2_comb %in% 7:8   ~ 2,  # $50k–$99k
    demo_comb_income_v2_comb == 10      ~ 4,  # > $200k
    demo_comb_income_v2_comb %in% c(5,6,9) ~ 3,  # everyone else
    demo_comb_income_v2_comb %in% c(777, 999) ~ NA_real_  # missing responses
  )) %>% 
  filter(!is.na(income_simple)) %>% 
  group_by(centile_cluster_km, income_simple) %>%
  summarize(count = n()) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = factor(centile_cluster_km), y = prop, fill = income_simple)) +
  geom_col(position = "fill") +
  labs(title = "Income Proportions by Cluster",
       x = "Cluster",
       y = "Proportion")



```
```{r}

chi_sq_data <- thickness_centile_male_wider_na %>%
  left_join(thickness_centile_male_mh %>%
              group_by(src_subject_id) %>%
              summarize(demo_comb_income_v2_comb = first(na.omit(demo_comb_income_v2_comb)))
          , by = "src_subject_id") %>% 
  mutate(income_simple = case_when(
    demo_comb_income_v2_comb %in% 1:4   ~ 1,  # < $25k
    demo_comb_income_v2_comb %in% 7:8   ~ 2,  # $50k–$99k
    demo_comb_income_v2_comb == 10      ~ 4,  # > $200k
    demo_comb_income_v2_comb %in% c(5,6,9) ~ 3,  # everyone else
    demo_comb_income_v2_comb %in% c(777, 999) ~ NA_real_  # missing responses
  )) %>% 
  filter(!is.na(income_simple))

table_income <- table(chi_sq_data$centile_cluster_km,
                      chi_sq_data$income_simple)
chisq.test(table_income)
```

Let's begin getting individual residuals scores away from predicted gamlss model
```{r}
thickness_harmonized_male$fitted <- fitted(thickness_model21_male,
                                        what = "mu",
                                        type = "response")
thickness_harmonized_male$residual <- 
  thickness_harmonized_male$smri_thick_cdk_mean.combat - thickness_harmonized_male$fitted


```

