---
title: "longComBat"
author: Jeffrey Choi
output: html_document
---

Data preproccessing
```{r}
#| warning: false

# lets work with cortical thickness first
data_dir <- '/Users/jeffee/Library/CloudStorage/Box-Box/ABCD Tabulated Data/5.1/core/'

setwd(data_dir)

# LOAD DATA
# Demographic variables and propensity weights
demog <- read.csv("abcd-general/abcd_p_demo.csv", na.strings = c(999, 777))
# Age in months, Site ID (ABCD Study Design Variables), Family ID
study_covars <- read.csv("abcd-general/abcd_y_lt.csv")
# desikan atlas, cortical thickness
dat.mri.ct = read.csv('imaging/mri_y_smr_thk_dsk.csv')

list_of_ct_regions <- colnames(dat.mri.ct)[3:ncol(dat.mri.ct)] # this is important


# basic cleaning for demographic variables
demog_clean <- demog |>
  # select broad demographics
  select(src_subject_id, eventname, starts_with("demo_brthdat_v2"), demo_sex_v2, race_ethnicity) |>
  # fill in race and sex first (avoid losing demog info due to filtering eventname)
  group_by(src_subject_id) %>%
  mutate(
    race_ethnicity = first(na.omit(race_ethnicity)),
    demo_sex_v2 = first(na.omit(demo_sex_v2)),
    src_subject_id = factor(src_subject_id)
  ) %>%
  ungroup() %>%
  filter(eventname %in% c("baseline_year_1_arm_1", "2_year_follow_up_y_arm_1",
                          "4_year_follow_up_y_arm_1")) |>
  mutate(
    # clean age variable
    age = case_when(
      eventname == "baseline_year_1_arm_1" ~ trunc(demo_brthdat_v2), # remove decimals 
      eventname %in% c("2_year_follow_up_y_arm_1", "4_year_follow_up_y_arm_1") ~
        trunc(demo_brthdat_v2_l)),
    # broad race/ethnicity categories
    race_ethnicity = case_match(
      race_ethnicity,
      1 ~ "White",
      2 ~ "Black",
      3 ~ "Hispanic",
      4 ~ "Asian",
      5 ~ "Other"
    ),
    # recode sex variable
    sex = factor(demo_sex_v2),
    sex = fct_recode(
      sex,
      "Intersex-Male" = "3"
    )) %>%
  filter(eventname %in% c("baseline_year_1_arm_1", "2_year_follow_up_y_arm_1",
                          "4_year_follow_up_y_arm_1"))


thickness <- dat.mri.ct |>
  # join mri data to demographics
  left_join(demog_clean, by = join_by("eventname", "src_subject_id")) |>
  # join to study covariates
  left_join(study_covars, by = join_by("eventname", "src_subject_id")) |>
  select(src_subject_id, eventname, starts_with("smri"), age, sex, race_ethnicity 
         , site_id_l, interview_age) |>
  # remove ages less than 8 and more than 16
  filter(age < 16 & age > 8) |>
  mutate(interview_age = as.numeric(interview_age))

# create baseline age column for longComBat
baseline_ages <- thickness %>%
  mutate(baseline_age = interview_age / 12) %>%
  group_by(src_subject_id) %>%
  mutate(baseline_age = first(baseline_age)) %>%
  pull(baseline_age)

# removed single NA race and intersex individuals (3)
thickness <- thickness %>%
  mutate(baseline_age = baseline_ages) %>%
  filter(sex != "Intersex-Male") %>%
  filter(!is.na(race_ethnicity))
```

``` {r}
thickness %>%
  ggplot(aes(x = smri_thick_cdk_banksstslh, y = smri_thick_cdk_cdacatelh, color = site_id_l)) +
  geom_point() +
  theme_classic()
```
Implements longComBat
```{r}
simdata_combat <- longCombat(idvar='src_subject_id', 
                             timevar='interview_age',
                             batchvar='site_id_l', 
                             features=list_of_ct_regions, 
                             formula='sex + baseline_age',
                             ranef='(1|src_subject_id)',
                             data=thickness)
```
```{r}
thickness_harmonized <- simdata_combat$data_combat

thickness_harmonized <- thickness_harmonized %>% mutate(src_subject_id = factor(src_subject_id))

thickness_plus_harmonized <- merge(thickness, thickness_harmonized, by=c('src_subject_id', "interview_age"))

thickness_plus_harmonized <- thickness_plus_harmonized %>% mutate(src_subject_id = factor(src_subject_id))
```

Box Plot distributions before and after harmonization (mean corticol thickness)
```{r}
thickness_site_plot <- thickness %>% 
  ggplot(aes(x = site_id_l, y = smri_thick_cdk_mean)) +
  geom_boxplot() +
  labs(
    title = "Mean Cortical Thickness by Site",
    x = "Site",
    y = "Cortical Surface Area"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


thickness_site_plot_harm <- thickness_harmonized %>%
  ggplot(aes(x = site_id_l, y = smri_thick_cdk_mean.combat)) +
  geom_boxplot() +
  labs(
    title = "Mean Cortical Thickness by Site",
    subtitle = "longComBat Harmonized",
    x = "Site",
    y = "Cortical Surface Area"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

thickness_site_plot + thickness_site_plot_harm
```

longComBat provided Box Plots of residuals
```{r}
par(mfrow = c(1, 2))
boxplot_before_combat <- batchBoxplot(idvar='src_subject_id', 
                                      batchvar='site_id_l', 
                                      feature='smri_thick_cdk_mean', 
                                      formula='sex + baseline_age',
                                      ranef='(1|src_subject_id)',
                                      data=thickness,
                                      main = "Left plot")

boxplot_after_combat <- batchBoxplot(idvar='src_subject_id', 
                                     batchvar='site_id_l.y', 
                                     feature='smri_thick_cdk_mean.combat', 
                                     formula='sex + baseline_age',
                                     ranef='(1|src_subject_id)',
                                     data=thickness_plus_harmonized,
                                     main = "Right plot")
```

```{r}
# plot spaghetti plots of thickness
thickness %>%
  ggplot(aes(x = interview_age, y = smri_thick_cdk_mean, group = src_subject_id)) + 
  geom_line(color="azure3", alpha=0.2) + 
  geom_point(color="azure3", alpha = 0.2) +
  scale_x_continuous(
    name = "Age (years)",
    breaks = seq(96, 192, by = 12),
    labels = function(x) x / 12
  ) +
  labs(
    title = "Individual Corticol Thickness Over Time",
    y = "Corticol Thickness (mm)"
  ) +
  theme_minimal()

# plot spaghetti plots of thickness on sex
thickness %>%
  mutate(sex = ifelse(sex == 1, "Female", "Male")) %>%
  ggplot(aes(x = interview_age, y = smri_thick_cdk_mean, group = src_subject_id)) + 
  geom_line(color="azure3", alpha=0.2) + 
  geom_point(color="azure3", alpha = 0.2) +
  scale_x_continuous(
    name = "Age (years)",
    breaks = seq(96, 192, by = 12),
    labels = function(x) x / 12
  ) +
  labs(
    title = "Individual Corticol Thickness Over Time",
    y = "Corticol Thickness (mm)"
  ) +
  theme_minimal() + facet_grid(. ~ sex) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# plot spaghetti plots of thickness (longCombat)
thickness_plus_harmonized %>%
  ggplot(aes(x = interview_age, y = smri_thick_cdk_mean.combat, group = src_subject_id)) + 
  geom_line(color="azure3", alpha=0.2) + 
  geom_point(color="azure3", alpha = 0.2) +
  scale_x_continuous(
    name = "Age (Years)",
    breaks = seq(96, 192, by = 12),
    labels = function(x) x / 12
  ) +
  labs(
    title = "Individual Corticol Thickness Over Time",
    subtitle = "longComBat Harmonized",
    y = "Corticol Thickness (mm)"
  ) +
  theme_minimal()

# plot spaghetti plots of thickness on sex
thickness_plus_harmonized %>%
  mutate(sex = ifelse(sex == 1, "Female", "Male")) %>%
  ggplot(aes(x = interview_age, y = smri_thick_cdk_mean.combat, group = src_subject_id)) + 
  geom_line(color="azure3", alpha=0.2) + 
  geom_point(color="azure3", alpha = 0.2) +
  scale_x_continuous(
    name = "Age (years)",
    breaks = seq(96, 192, by = 12),
    labels = function(x) x / 12
  ) +
  labs(
    title = "Individual Corticol Thickness Over Time",
    subtitle = "longComBat Harmonized",
    y = "Corticol Thickness (mm)"
  ) +
  theme_minimal() + facet_grid(. ~ sex) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

```

Beginning model distribution search

## Model 1 - family: Box-Cox t
```{r}
# WHAT DOES THIS DO 
lms_model <- lms(smri_thick_cdk_mean.combat, 
                 interview_age, 
                 data = thickness_harmonized, 
                 trans.x = TRUE, 
                 k = 2)

# grabs degrees of freedom
lms_mu.nl.df <- lms_model$mu.nl.df
lms_sigma.nl.df <- lms_model$sigma.nl.df
lms_tau.nl.df <- lms_model$tau.nl.df
lms_nu.nl.df <- lms_model$nu.nl.df

# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model1 <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
```

## Model 1 Statistics - family: Box-Cox t
```{r}
#| warning: false

summary(thickness_model1)

fitted_centiles_legend(
  thickness_model1,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model1,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model1, xvar = thickness_harmonized$interview_age)
```
```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model1)

print("Bayesian Information Criterion:")
GAIC(thickness_model1, k = log(nrow(thickness_harmonized)))

```






## Model 2 - family: Box-Cox t original
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model2 <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCTo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
```
## Model 2 Statistics - family: Box-Cox t original
```{r}
#| warning: false

summary(thickness_model2)

fitted_centiles_legend(
  thickness_model2,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model2,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model2, xvar = thickness_harmonized$interview_age)
```

```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model2)

print("Bayesian Information Criterion:")
GAIC(thickness_model2, k = log(nrow(thickness_harmonized)))
```


## Model 3 - family: Box-Cox power exp. original
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model3 <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
```

## Model 3 Statistics - family: Box-Cox power exp. original
```{r}
#| warning: false

summary(thickness_model3)

fitted_centiles_legend(
  thickness_model3,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model3,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model3, xvar = thickness_harmonized$interview_age)
```

```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model3)

print("Bayesian Information Criterion:")
GAIC(thickness_model3, k = log(nrow(thickness_harmonized)))
```

## Model 4 - family: Box-Cox power exp
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model4 <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
```

## Model 4 Statistics - family: Box-Cox power exp.
```{r}
#| warning: false

summary(thickness_model4)

fitted_centiles_legend(
  thickness_model4,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model4,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model4, xvar = thickness_harmonized$interview_age)
```

```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model4)

print("Bayesian Information Criterion:")
GAIC(thickness_model4, k = log(nrow(thickness_harmonized)))
```

## Model 5 - family: Box-Cox t (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model5 <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age^lms_model$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
```

## Model 5 Statistics - family: Box-Cox t (power transformation on predictor)
```{r}
#| warning: false

summary(thickness_model5)

fitted_centiles_legend(
  thickness_model5,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model5,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model5, xvar = thickness_harmonized$interview_age)
```

```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model5)

print("Bayesian Information Criterion:")
GAIC(thickness_model5, k = log(nrow(thickness_harmonized)))
```
## Model 6 - family: Box-Cox t original (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model6 <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age^lms_model$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCTo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
```
## Model 6 Statistics - family: Box-Cox t original (power transformation on predictor)
```{r}
#| warning: false

summary(thickness_model6)

fitted_centiles_legend(
  thickness_model6,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model6,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model6, xvar = thickness_harmonized$interview_age)
```

```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model6)

print("Bayesian Information Criterion:")
GAIC(thickness_model6, k = log(nrow(thickness_harmonized)))
```

## Model 7 - family: Box-Cox power exp. original (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model7 <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age^lms_model$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
```

## Model 7 Statistics - family: Box-Cox power exp. original (power transformation on predictor)
```{r}
#| warning: false

summary(thickness_model7)

fitted_centiles_legend(
  thickness_model7,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model7,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model7, xvar = thickness_harmonized$interview_age)
```

```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model7)

print("Bayesian Information Criterion:")
GAIC(thickness_model7, k = log(nrow(thickness_harmonized)))
```

## Model 8 - family: Box-Cox power exp (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
thickness_model8 <- gamlss(
  smri_thick_cdk_mean.combat ~ pb(interview_age^lms_model$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
```

## Model 8 Statistics - family: Box-Cox power exp. (power transformation of predictor)
```{r}
#| warning: false

summary(thickness_model8)

fitted_centiles_legend(
  thickness_model8,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model8,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model8, xvar = thickness_harmonized$interview_age)
```

```{r}
print("Generalized A (powerkaike Information Criterion:")
GAIC(thickness_model8)

print("Bayesian Information Criterion:")
GAIC(thickness_model8, k = log(nrow(thickness_harmonized)))
```