---
title: "Brain_regions_modelled"
output: html_notebook
---

Data preproccessing
```{r}
library(tidyverse)
library(lmerTest)
library(janitor)
library(patchwork)

#| warning: false

# lets work with cortical thickness first
data_dir <- '~/Library/CloudStorage/Box-Box/ABCD Tabulated Data/5.1/core'

setwd(data_dir)

# LOAD DATA
# Demographic variables and propensity weights
demog <- read.csv("abcd-general/abcd_p_demo.csv", na.strings = c(999, 777))
# Age in months, Site ID (ABCD Study Design Variables), Family ID
study_covars <- read.csv("abcd-general/abcd_y_lt.csv")

# desikan atlas, cortical thickness
dat.mri.ct = read.csv('imaging/mri_y_smr_area_dsk.csv') # this gets the file containing measurements for entorhinal brain region

list_of_ct_regions <- colnames(dat.mri.ct)[3:ncol(dat.mri.ct)] # this is important

# basic cleaning for demographic variables
demog_clean <- demog |>
  # select broad demographics
  select(src_subject_id, eventname, starts_with("demo_brthdat_v2"), demo_sex_v2, race_ethnicity) |>
  # fill in race and sex first (avoid losing demog info due to filtering eventname)
  group_by(src_subject_id) %>%
  mutate(
    race_ethnicity = first(na.omit(race_ethnicity)),
    demo_sex_v2 = first(na.omit(demo_sex_v2)),
    src_subject_id = factor(src_subject_id)
  ) %>%
  ungroup() %>%
  filter(eventname %in% c("baseline_year_1_arm_1", "2_year_follow_up_y_arm_1",
                          "4_year_follow_up_y_arm_1")) |>
  mutate(
    # clean age variable
    age = case_when(
      eventname == "baseline_year_1_arm_1" ~ trunc(demo_brthdat_v2), # remove decimals 
      eventname %in% c("2_year_follow_up_y_arm_1", "4_year_follow_up_y_arm_1") ~
        trunc(demo_brthdat_v2_l)),
    # broad race/ethnicity categories
    race_ethnicity = case_match(
      race_ethnicity,
      1 ~ "White",
      2 ~ "Black",
      3 ~ "Hispanic",
      4 ~ "Asian",
      5 ~ "Other"
    ),
    # recode sex variable
    sex = factor(demo_sex_v2),
    sex = fct_recode(
      sex,
      "Intersex-Male" = "3"
    )) %>%
  filter(eventname %in% c("baseline_year_1_arm_1", "2_year_follow_up_y_arm_1",
                          "4_year_follow_up_y_arm_1"))

thickness <- dat.mri.ct |>
  # join mri data to demographics
  left_join(demog_clean, by = join_by("eventname", "src_subject_id")) |>
  # join to study covariates
  left_join(study_covars, by = join_by("eventname", "src_subject_id")) |>
  select(src_subject_id, eventname, starts_with("smri"), age, sex, race_ethnicity 
         , site_id_l, interview_age) |>
  # remove ages less than 8 and more than 16
  filter(age < 16 & age > 8) |>
  mutate(interview_age = as.numeric(interview_age))

# create baseline age column for longComBat
baseline_ages <- thickness %>%
  mutate(baseline_age = interview_age / 12) %>%
  group_by(src_subject_id) %>%
  mutate(baseline_age = first(baseline_age)) %>%
  pull(baseline_age)

# removed single NA race and intersex individuals (3)
thickness <- thickness %>%
  mutate(baseline_age = baseline_ages) %>%
  filter(sex != "Intersex-Male") %>%
  filter(!is.na(race_ethnicity))
```


``` {r}
thickness %>%
  ggplot(aes(x = smri_area_cdk_banksstslh, y = smri_area_cdk_cdacatelh, color = site_id_l)) + 
  geom_point() +
  theme_classic()
```
#### Implements longComBat
```{r}
detach("package:tidyverse", unload=TRUE)

#library(devtools)
#devtools::install_github("jcbeer/longCombat")
library(longCombat)

simdata_combat <- longCombat(idvar='src_subject_id', 
                             timevar='interview_age',
                             batchvar='site_id_l', 
                             features=list_of_ct_regions, 
                             formula='sex + baseline_age',
                             ranef='(1|src_subject_id)',
                             data=thickness)
```


### joins datasets
```{r}
area_harmonized <- simdata_combat$data_combat
area_plus_harmonized <- merge(thickness, area_harmonized, by=c('src_subject_id', "interview_age"))

area_plus_harmonized <- area_plus_harmonized %>% mutate(src_subject_id = factor(src_subject_id))

# adds sex and other cols
area_harmonized <- area_plus_harmonized %>%
  select(-matches("^smri(?!.*\\.combat$)", perl = TRUE)) %>% 
  mutate(src_subject_id = factor(src_subject_id))

```

### creates subset of data base on sex, Male and Female.
```{r}
area_harmonized_male <- area_harmonized %>% filter(sex == 2)
area_harmonized_female <- area_harmonized %>% filter(sex == 1)

lms_model_m <- lms(smri_area_cdk_total.combat, 
                 interview_age, 
                 data = area_harmonized_male, 
                 trans.x = TRUE, 
                 k = 2)

lms_model_f <- lms(smri_area_cdk_total.combat, 
                 interview_age, 
                 data = area_harmonized_female, 
                 trans.x = TRUE, 
                 k = 2)

# grabs degrees of freedom
lms_mu_m.nl.df <- lms_model_m$mu.nl.df
lms_sigma_m.nl.df <- lms_model_m$sigma.nl.df
lms_tau_m.nl.df <- lms_model_m$tau.nl.df
lms_nu_m.nl.df <- lms_model_m$nu.nl.df


lms_mu_f.nl.df <- lms_model_f$mu.nl.df
lms_sigma_f.nl.df <- lms_model_f$sigma.nl.df
lms_tau_f.nl.df <- lms_model_f$tau.nl.df
lms_nu_f.nl.df <- lms_model_f$nu.nl.df
```

#############__________________________############################_____________######################################

## Model 9 - family: Box-Cox t
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model9_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_m.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_m.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_m.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_m.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model9_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_f.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_f.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_f.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_f.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 9 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model9_male)

fitted_centiles_legend(
  area_model9_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model9_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model9_male, xvar = area_harmonized_male$interview_age)


## Model 9 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model9_female)

fitted_centiles_legend(
  area_model9_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model9_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model9_female, xvar = area_harmonized_female$interview_age)
```

## Model 10 - family: Box-Cox t original
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model10_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_m.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_m.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_m.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_m.nl.df),
  
  family = BCTo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model10_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_f.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_f.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_f.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_f.nl.df),
  
  family = BCTo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 10 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model10_male)

fitted_centiles_legend(
  area_model10_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical area (mm)") +
  theme_minimal()

round(Q.stats(
  area_model10_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model10_male, xvar = area_harmonized_male$interview_age)


## Model 10 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model10_female)

fitted_centiles_legend(
  area_model10_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical area (mm)") +
  theme_minimal()

round(Q.stats(
  area_model10_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model10_female, xvar = area_harmonized_female$interview_age)
```

## Model 11 - family: Box-Cox power exp. original
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model11_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_m.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_m.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_m.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_m.nl.df),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model11_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_f.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_f.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_f.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_f.nl.df),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 11 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model11_male)

fitted_centiles_legend(
  area_model24_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model11_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model11_male, xvar = area_harmonized_male$interview_age)


## Model 11 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model11_female)

fitted_centiles_legend(
  area_model11_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model11_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model11_female, xvar = area_harmonized_female$interview_age)
```
## Model 12 - family: Box-Cox power exp
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model12_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_m.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_m.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_m.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_m.nl.df),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model12_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_f.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_f.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_f.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_f.nl.df),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 12 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model12_male)

fitted_centiles_legend(
  area_model12_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model12_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model12_male, xvar = area_harmonized_male$interview_age)


## Model 12 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model12_female)

fitted_centiles_legend(
  area_model12_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model12_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model12_female, xvar = area_harmonized_female$interview_age)
```
## Model 13 - family: Box-Cox t (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model13_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_m.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_m.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_m.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_m.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model13_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_f.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_f.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_f.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_f.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 13 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model13_male)

fitted_centiles_legend(
  area_model13_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model13_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model13_male, xvar = area_harmonized_male$interview_age)


## Model 13 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model13_female)

fitted_centiles_legend(
  area_model13_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model13_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model13_female, xvar = area_harmonized_female$interview_age)
```
## Model 14 - family: Box-Cox t original (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model14_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_m.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_m.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_m.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_m.nl.df),
  
  family = BCTo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model14_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_f.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_f.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_f.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_f.nl.df),
  
  family = BCTo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 14 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model14_male)

fitted_centiles_legend(
  area_model14_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model14_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model14_male, xvar = area_harmonized_male$interview_age)


## Model 14 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model14_female)

fitted_centiles_legend(
  area_model14_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model14_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model14_female, xvar = area_harmonized_female$interview_age)
```
## Model 15 - family: Box-Cox power exp. original (power transformation on predictor) 
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model15_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_m.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_m.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_m.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_m.nl.df),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model15_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_f.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_f.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_f.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_f.nl.df),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 15 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model15_male)

fitted_centiles_legend(
  area_model15_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model15_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model15_male, xvar = area_harmonized_male$interview_age)


## Model 15 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model15_female)

fitted_centiles_legend(
  area_model15_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model15_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model15_female, xvar = area_harmonized_female$interview_age)
```
## Model 16 - family: Box-Cox power exp (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model16_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_m.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_m.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_m.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_m.nl.df),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model16_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu_f.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma_f.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu_f.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau_f.nl.df),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 16 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model16_male)

fitted_centiles_legend(
  area_model16_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model16_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model16_male, xvar = area_harmonized_male$interview_age)


## Model 16 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model16_female)

fitted_centiles_legend(
  area_model16_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model16_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model16_female, xvar = area_harmonized_female$interview_age)
```
## Model 17 - family: Box-Cox t
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model17_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model17_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 17 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model17_male)

fitted_centiles_legend(
  area_model17_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model17_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model17_male, xvar = area_harmonized_male$interview_age)


## Model 17 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model17_female)

fitted_centiles_legend(
  area_model17_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model17_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model17_female, xvar = area_harmonized_female$interview_age)
```
## Model 18 - family: Box-Cox t original
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model18_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCTo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model18_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCTo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 18 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model18_male)

fitted_centiles_legend(
  area_model18_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model18_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model18_male, xvar = area_harmonized_male$interview_age)


## Model 18 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model18_female)

fitted_centiles_legend(
  area_model18_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model18_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model18_female, xvar = area_harmonized_female$interview_age)
```
## Model 19 - family: Box-Cox power exp. original
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model19_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model19_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 19 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model19_male)

fitted_centiles_legend(
  area_model19_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model19_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model24_male, xvar = area_harmonized_male$interview_age)


## Model 24 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model19_female)

fitted_centiles_legend(
  area_model19_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model19_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model19_female, xvar = area_harmonized_female$interview_age)
```
## Model 20 - family: Box-Cox power exp
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model20_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model20_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 20 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model20_male)

fitted_centiles_legend(
  area_model20_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model20_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model20_male, xvar = area_harmonized_male$interview_age)


## Model 20 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model20_female)

fitted_centiles_legend(
    area_model20_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model20_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model20_female, xvar = area_harmonized_female$interview_age)
```
## Model 21 - family: Box-Cox t (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model21_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model21_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 21 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model21_male)

fitted_centiles_legend(
  area_model21_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model21_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model21_male, xvar = area_harmonized_male$interview_age)


## Model 21 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model21_female)

fitted_centiles_legend(
  area_model21_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model21_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model21_female, xvar = area_harmonized_female$interview_age)
```
## Model 22 - family: Box-Cox t original (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model22_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCTo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model22_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_f$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 22 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model22_male)

fitted_centiles_legend(
  area_model22_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model22_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model22_male, xvar = area_harmonized_male$interview_age)


## Model 22 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model22_female)

fitted_centiles_legend(
  area_model22_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model22_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model22_female, xvar = area_harmonized_female$interview_age)
```
## Model 23 - family: Box-Cox power exp. original (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model23_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model23_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCPEo(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 23 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model23_male)

fitted_centiles_legend(
  area_model23_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model23_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model23_male, xvar = area_harmonized_male$interview_age)


## Model 23 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model23_female)

fitted_centiles_legend(
  area_model23_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model23_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model23_female, xvar = area_harmonized_female$interview_age)
```
## Model 24 - family: Box-Cox power exp (power transformation on predictor)
```{r}
# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model24_male <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_m$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_male)

# initial model for average thickness using gamlss
# P-spline smoothing functions
area_model24_female <- gamlss(
  smri_area_cdk_total.combat ~ pb(interview_age^lms_model_f$power) + gamlss::random(src_subject_id), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  sigma.formula =~ cs(interview_age),
  
  family = BCPE(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = area_harmonized_female)


## Model 24 Male Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model24_male)

fitted_centiles_legend(
  area_model24_male,
  cent = c(2.5, 50, 97.5),
  xvar = area_harmonized_male %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model24_male,
  xvar = area_harmonized_male$interview_age,
  zvals = FALSE), 3)

wp(area_model24_male, xvar = area_harmonized_male$interview_age)


## Model 24 Female Statistics - family: Box-Cox power exp. (power transformation on predictor)

#| warning: false

summary(area_model24_female)

fitted_centiles_legend(
  area_model24_female,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized_female %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  area_model24_female,
  xvar = area_harmonized_female$interview_age,
  zvals = FALSE), 3)

wp(area_model24_female, xvar = area_harmonized_female$interview_age)
```

```{r}
print("Model 9: Generalized Akaike Information Criterion:")
GAIC(area_model9_male)
GAIC(area_model9_female)

print("Model 10: Generalized Akaike Information Criterion:")
GAIC(area_model10_male)
GAIC(area_model10_female)

print("Model 11: Generalized Akaike Information Criterion:")
GAIC(area_model11_male)
GAIC(area_model11_female)

print("Model 12: Generalized Akaike Information Criterion:")
GAIC(area_model12_male)
GAIC(area_model12_female)

print("Model 13: Generalized Akaike Information Criterion:")
GAIC(area_model13_male)
GAIC(area_model13_female)

print("Model 14: Generalized Akaike Information Criterion:")
GAIC(area_model14_male)
GAIC(area_model14_female)

print("Model 15: Generalized Akaike Information Criterion:")
GAIC(area_model15_male)
GAIC(area_model15_female)

print("Model 16: Generalized Akaike Information Criterion:")
GAIC(area_model16_male)
GAIC(area_model16_female)

print("Model 17: Generalized Akaike Information Criterion:")
GAIC(area_model17_male)
GAIC(area_model17_female)

print("Model 18: Generalized Akaike Information Criterion:")
GAIC(area_model18_male)
GAIC(area_model18_female)

print("Model 19: Generalized Akaike Information Criterion:")
GAIC(area_model19_male)
GAIC(area_model19_female)

print("Model 20: Generalized Akaike Information Criterion:")
GAIC(area_model20_male)
GAIC(area_model20_female)

print("Model 21: Generalized Akaike Information Criterion:")
GAIC(area_model21_male)
GAIC(area_model21_female)

print("Model 22: Generalized Akaike Information Criterion:")
GAIC(area_model22_male)
GAIC(area_model22_female)

print("Model 23: Generalized Akaike Information Criterion:")
GAIC(area_model23_male)
GAIC(area_model23_female)

print("Model 24: Generalized Akaike Information Criterion:")
GAIC(area_model24_male)
GAIC(area_model24_female)
```

Box-Cox t models have good mean on average on the q statistics on average. Good worms plots, some have convex? downward shape on bottom right

Box-Cox t original has more spotty q statsitcs. less consistant. good worm plots, ends behaving more pattern like and extreme

Box-Cox power exp orig has less not extreme q statsitics, extremeties still exist. worms plots similar to box cox t

we decide on box cox power exp, model 20 as it is the most simple, all GAIC are comparible