---
title: "Brain_regions_modelled"
output: html_notebook
---

Data preproccessing
```{r}
library(tidyverse)
library(lmerTest)
library(janitor)
library(patchwork)

#| warning: false

# lets work with cortical thickness first
data_dir <- '~/Library/CloudStorage/Box-Box/ABCD Tabulated Data/5.1/core'

setwd(data_dir)

# LOAD DATA
# Demographic variables and propensity weights
demog <- read.csv("abcd-general/abcd_p_demo.csv", na.strings = c(999, 777))
# Age in months, Site ID (ABCD Study Design Variables), Family ID
study_covars <- read.csv("abcd-general/abcd_y_lt.csv")

# desikan atlas, cortical thickness
dat.mri.ct = read.csv('imaging/mri_y_smr_thk_dsk.csv') # this gets the file containing measurements for entorhinal brain region

list_of_ct_regions <- colnames(dat.mri.ct)[3:ncol(dat.mri.ct)] # this is important

# basic cleaning for demographic variables
demog_clean <- demog |>
  # select broad demographics
  select(src_subject_id, eventname, starts_with("demo_brthdat_v2"), demo_sex_v2, race_ethnicity) |>
  # fill in race and sex first (avoid losing demog info due to filtering eventname)
  group_by(src_subject_id) %>%
  mutate(
    race_ethnicity = first(na.omit(race_ethnicity)),
    demo_sex_v2 = first(na.omit(demo_sex_v2)),
    src_subject_id = factor(src_subject_id)
  ) %>%
  ungroup() %>%
  filter(eventname %in% c("baseline_year_1_arm_1", "2_year_follow_up_y_arm_1",
                          "4_year_follow_up_y_arm_1")) |>
  mutate(
    # clean age variable
    age = case_when(
      eventname == "baseline_year_1_arm_1" ~ trunc(demo_brthdat_v2), # remove decimals 
      eventname %in% c("2_year_follow_up_y_arm_1", "4_year_follow_up_y_arm_1") ~
        trunc(demo_brthdat_v2_l)),
    # broad race/ethnicity categories
    race_ethnicity = case_match(
      race_ethnicity,
      1 ~ "White",
      2 ~ "Black",
      3 ~ "Hispanic",
      4 ~ "Asian",
      5 ~ "Other"
    ),
    # recode sex variable
    sex = factor(demo_sex_v2),
    sex = fct_recode(
      sex,
      "Intersex-Male" = "3"
    )) %>%
  filter(eventname %in% c("baseline_year_1_arm_1", "2_year_follow_up_y_arm_1",
                          "4_year_follow_up_y_arm_1"))

thickness <- dat.mri.ct |>
  # join mri data to demographics
  left_join(demog_clean, by = join_by("eventname", "src_subject_id")) |>
  # join to study covariates
  left_join(study_covars, by = join_by("eventname", "src_subject_id")) |>
  select(src_subject_id, eventname, starts_with("smri"), age, sex, race_ethnicity 
         , site_id_l, interview_age) |>
  # remove ages less than 8 and more than 16
  filter(age < 16 & age > 8) |>
  mutate(interview_age = as.numeric(interview_age))

# create baseline age column for longComBat
baseline_ages <- thickness %>%
  mutate(baseline_age = interview_age / 12) %>%
  group_by(src_subject_id) %>%
  mutate(baseline_age = first(baseline_age)) %>%
  pull(baseline_age)

# removed single NA race and intersex individuals (3)
thickness <- thickness %>%
  mutate(baseline_age = baseline_ages) %>%
  filter(sex != "Intersex-Male") %>%
  filter(!is.na(race_ethnicity))
```


``` {r}
thickness %>%
  ggplot(aes(x = smri_thick_cdk_banksstslh, y = smri_thick_cdk_cdacatelh, color = site_id_l)) + 
  geom_point() +
  theme_classic()
```
Implements longComBat
```{r}
detach("package:tidyverse", unload=TRUE)

#library(devtools)
#devtools::install_github("jcbeer/longCombat")
library(longCombat)

simdata_combat <- longCombat(idvar='src_subject_id', 
                             timevar='interview_age',
                             batchvar='site_id_l', 
                             features=list_of_ct_regions, 
                             formula='sex + baseline_age',
                             ranef='(1|src_subject_id)',
                             data=thickness)
```
```{r}
thickness_harmonized <- simdata_combat$data_combat
View(thickness_harmonized)
thickness_plus_harmonized <- merge(thickness, thickness_harmonized, by=c('src_subject_id', "interview_age"))

thickness_plus_harmonized <- thickness_plus_harmonized %>% mutate(src_subject_id = factor(src_subject_id))
View(thickness_plus_harmonized)
```


implement model 5 for Cortical thickness in mm of APARC ROI lh-superiorfrontal
```{r}
thickness_model5 <- gamlss(
  smri_thick_cdk_sufrlh.combat ~ pb(interview_age^lms_model$power) + gamlss::random(factor(src_subject_id)), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
View(thickness_model5)
```

## Model 5 Statistics - family: Box-Cox t (power transformation on predictor)
```{r}
#| warning: false

summary(thickness_model5)

fitted_centiles_legend(
  thickness_model5,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model5,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model5, xvar = thickness_harmonized$interview_age)
```
```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model5)

print("Bayesian Information Criterion:")
GAIC(thickness_model5, k = log(nrow(thickness_harmonized)))
```


 
############### new region

implement model 5 for Cortical thickness in mm of APARC ROI lh-superiorparietal
```{r}
thickness_model5 <- gamlss(
  smri_thick_cdk_supllh.combat ~ pb(interview_age^lms_model$power) + gamlss::random(factor(src_subject_id)), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
View(thickness_model5)
```

## Model 5 Statistics - family: Box-Cox t (power transformation on predictor)
```{r}
#| warning: false

summary(thickness_model5)

fitted_centiles_legend(
  thickness_model5,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model5,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model5, xvar = thickness_harmonized$interview_age)
```
```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model5)

print("Bayesian Information Criterion:")
GAIC(thickness_model5, k = log(nrow(thickness_harmonized)))
```


################ new region

implement model 5 for Cortical thickness in mm of APARC ROI lh-superiorparietal
```{r}
thickness_model5 <- gamlss(
  smri_thick_cdk_insulalh.combat ~ pb(interview_age^lms_model$power) + gamlss::random(factor(src_subject_id)), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
View(thickness_model5)
```

## Model 5 Statistics - family: Box-Cox t (power transformation on predictor)
```{r}
#| warning: false

summary(thickness_model5)

fitted_centiles_legend(
  thickness_model5,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model5,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model5, xvar = thickness_harmonized$interview_age)
```
```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model5)

print("Bayesian Information Criterion:")
GAIC(thickness_model5, k = log(nrow(thickness_harmonized)))
```


################ new region

implement model 5 for Cortical thickness in mm of APARC ROI rh-inferiorparietal
```{r}
thickness_model5 <- gamlss(
  smri_thick_cdk_ifplrh.combat ~ pb(interview_age^lms_model$power) + gamlss::random(factor(src_subject_id)), # random subject effect
  # mu, sigma, nu, tau with cubic splines with previously collected degrees of freedom
  mu.formula =~ cs(interview_age, df = lms_mu.nl.df), 
  sigma.formula =~ cs(interview_age, df = lms_sigma.nl.df),
  nu.formula =~ cs(interview_age, df = lms_nu.nl.df),
  tau.formula =~ cs(interview_age, df = lms_tau.nl.df),
  
  family = BCT(mu.link = "log", # to stay positive
               sigma.link = "log", # to stay positive
               nu.link = "identity", 
               tau.link = "identity"), 
  data = thickness_harmonized)
View(thickness_model5)
```

## Model 5 Statistics - family: Box-Cox t (power transformation on predictor)
```{r}
#| warning: false

summary(thickness_model5)

fitted_centiles_legend(
  thickness_model5,
  cent = c(2.5, 50, 97.5),
  xvar = thickness_harmonized %>% dplyr::select(interview_age) %>% pull) +
  labs(x = "Interview Age (Months)",
       y = "Cortical Thickness (mm)") +
  theme_minimal()

round(Q.stats(
  thickness_model5,
  xvar = thickness_harmonized$interview_age), 3)

wp(thickness_model5, xvar = thickness_harmonized$interview_age)
```
```{r}
print("Generalized Akaike Information Criterion:")
GAIC(thickness_model5)

print("Bayesian Information Criterion:")
GAIC(thickness_model5, k = log(nrow(thickness_harmonized)))
```

